\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
%\usepackage{indentfirst}
\usepackage[margin=0.8in]{geometry}

\titleformat{\section}
{\Large\sc}{}{0em}{}
[\titlerule]

\titleformat{\subsection}
{\bfseries}{}{0em}{}
\titlespacing{\subsection}
{0em}{.5em}{0em}

\titleformat{\subsubsection}[runin]
{\bfseries}{}{0em}{}

\titlespacing{\subsubsection}
{0em}{.25em}{1em}

\renewcommand{\maketitle}{
\begin{center}
{\huge\sc
\theauthor}

\vspace{.25em}

rickyoswald@protonmail.com --- 07484 801960
\end{center}
}

\begin{document}

\title{R\'esum\'e}
\author{Ricky Valentine Oswald}

\maketitle

\section{Personal}
I have been interested in computers and technology since childhood, and wrote my first programs with Microsoft's QBasic when I was 12 years old.  I went on to study at College and University focusing on games programming, which I employed in several successful roles, and expanded into back-end web development for national healthcare.  In recent years my focus has shifted away from games and I've spent much of my spare time with GNU/Linux and other free software projects, gaining appreciation of technical, community, and licencing aspects of development.  I have some experience with low-level languages, even briefly studying the implementation of instruction sets in hardware.  Structured languages such as C++ and the Object-Oriented approach are definitely my comfort area, but I like to think I am language and system agnostic.

Outside of computing I enjoy studying Astronomy and Rocketry, with a focus on Orbital Mechanics.  I enjoy film critique, mostly of Sci-fi and Japanese Animation; my love of the latter has lead me to learn Japanese as a second language, and sparked an interest in linguistics in general.  I have a decent foundation in music theory and play the piano.  I reguarly cycle and spend some of my time in the garden growing my own food.

\section{Key Skills}
\subsubsection{Programming}
C, C++, C\#, Java, ActionScript 3, Shell, Python, Visual Basic, Lisp
\subsubsection{Web}
PHP, Javascript, Apache, MySQL, SOAP
\subsubsection{Markup}
HTML, XML, CSS, {\LaTeX}
\subsubsection{Operating Systems}
Linux, Windows, MacOS, Android, iOS
\subsubsection{Other}
GPG, Regex, nmap, netcat, DirectX, OpenGL
\subsubsection{Workflow}
Vim and terminal with a tiling window manager. Git and SSH for remote machines.

\section{Employment History}
\subsection{Liz Earle Union Bistro, 2019 to Present}
Working in the staff bistro, my responsobilities have included preparing food for staff and visitors, clearing and cleaning the cutlery and crockery, and cleaning the kitchen and equipment to a high standard.  I have been required to be flexible and prepared for large events and unexpected influx of visitors.
\subsection{The Dairyman's Daughter, 2018 to 2019}
Working in a busy kitchen environment I have demonstrated the ability to work to a high standard whilst under pressure.  My responsobilities include inspection and cleaning of kitchen utilities as well as assisting with food preparation and any other tasks required by the chefs.
\subsection{Pinnacle Systems Management, Software Developer, 2016 to 2018}
In a growing department with few developers, I delivered bespoke solutions for national healthcare.  Primarily involved in integration work for hospitals and pharmacies, I also supported the development of the web platform PharmOutcomes.  In this role I demonstrated the ability to liaise with multiple clients and users, and deliver solutions to a range of problems.
\subsection{YMCA Lake, Domestic Assistant, 2016}
Worked in a busy nursery, actvity center and officies, cleaning several areas to a high standard.  I was responsible for reporting stock levels and demonstrated the ability to carry out my duties without disturbing the ongoing activities of others.
\subsection{MonkeyPants Studio, Managing Director, 2015 to 2016}
Attempted to start and run my own games company from scratch, I was responsible for the estabilshment and financing of the business, including seeking investments and enlisting the assistance of a business mentor through established government scheemes.  Using primarily Unity/C\# and Adobe AIR, I worked as lead Software Developer and spent time reaching out to artists, musicians, and other collaborators.
\subsection{Kingswood Activity Center, Domestic Assistant, 2015}
Whilst getting MonkeyPants Studio off the ground I worked with a team at a busy activity center, cleaning the accommodation and facilities.  Demonstrated the ability to maintain a high standard with a  strict deadline.
\subsection{Oak Games, Software Developer, 2012 to 2014}
Worked in a small team developing computer games.  Initially for the Amazon Kindle eReader in which several of our titles dominated the charts.  After support for the eReader app store was discontinued by Amazon we moved into mobile development, first natively for Android and later Adobe AIR for Android and iOS.  I worked as the lead developer porting Odd Socks from Desktop to Mobile.
\subsection{Frontline Cleaning, Domestic Assistant, 2008 to 2009}
Whilst studying at University I worked in a children's nursery after-hours doing domestic level cleaning.  I was responsible for maintaining the stock levels and ensuring the nursery was cleaned to a high standard.
\subsection{Island Harbor, Barperson, 2007}
Demonstrated excellent customer service skills, maintaining bar stock levels, cash handling, and telephone enquiries.  Strong team player in a busy environment, I was offered a promotion to Bar Manager.
\subsection{Solar South, Telesales, 2006}
Met weekly targets in a high pressure environment, I primarily worked on generating new leads and booking home visits.
\subsection{David L. Watson, Database Developer, 2003}
With a colleague from College, developed an Access Database with VB6 front end to replace an existing paper based auditing system for a Computer Forensics and Data Recovery company.

\section{Education}
\subsection{University}
Computer Games Programming at Huddersfield Univeristy, 2008 to 2012.
\subsection{College}
BTEC Level 3 HND I.T. Practitioners at Isle of Wight College, 2004.

C\&G Level 2 Diploma for IT Users, 2003.

C\&G Visual Basic Level 1 Certificate, 2002.
\subsection{Music}
Royal Schools of Music Grade 3 Piano, 2004.
\subsection{School}
GCSEs (core) and GNVQ Business Studies at Sandown High School, 1999 to 2002.

\section{References}
\subsection{Mr. Luke Turvey}
Head Chef at Liz Earle.  luketurvey@mail.com - 07949 334607
\subsection{Mr. Dave Walker}
Managing Director at Oak Games.  dave@oakgames.co.uk - 07706 869574
\subsection{Mr. Henry Trotman}
Recruitment Consultant at Pertemps.  henry.trotman@pertemps.co.uk
\subsection{Dr. Duke Gledhill}
Huddersfield University.  d.gledhill@hud.ac.uk - 01484 472758

\end{document}
